---
title: "Time, Temp and additional Parameters Analysis"
author: "Melissa Schussman"
date: "2/24/2022"
output: html_document
---
Shared OneDrive is synchronized on my local machine in the directory `~/OneDrive - UWM/'. It must not be the case for your computer,  will thus have to change slightly the path to access the files. 
###Time and Temperature analysis 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=FALSE, include=FALSE}
#clear workspace
rm(list=ls(all=FALSE))
ls()
set.seed(123)
```


```{r echo=FALSE, include=FALSE}
#import libraries for data analysis
library(data.table)
library(dplyr)
library(reshape2)
library(pander)
require(gridExtra)
library(ggpubr)
library(tidyverse)      
library(lubridate)     
library(fpp2)         
library(zoo)            
library(openxlsx)
library(ggplot2)
library(rstatix)
library(cowplot)
library(ggplot2)



```


```{r echo=FALSE, include=FALSE}

#import data

#import data - all data from 8/25/20-8/25/21
library(readxl)
SARSConcPerCase <- openxlsx::read.xlsx("~/OneDrive - UWM/Melissa-neighborhoods/final thesis/travel time paper/JI.SS.all.xlsx", sheet = "noLOD", colNames = TRUE) 
head(SARSConcPerCase, 3)

#confirm date format
Date <- openxlsx::convertToDate(SARSConcPerCase$SampleCollectDate)

#set WWTP as factor
SARSConcPerCase$WWTPName<-as.factor(SARSConcPerCase$WWTPName)
levels(SARSConcPerCase$WWTPName)
SARSConcPerCase <-subset(SARSConcPerCase, WWTPName == "Milwaukee Jones Island" | WWTPName == "Milwaukee South Shore")

```


#SARS-CoV-2 Copies per case
```{r echo=FALSE}

ggplot(SARSConcPerCase, aes(Date, Conc_Capita)) +
  geom_point(aes(colour=`WWTPName`)) +
  facet_wrap( ~ `WWTPName`) +
  ggtitle("Average SARS-CoV-2 Copies per Case")

mean.data <- SARSConcPerCase %>%
  group_by(`WWTPName`) %>%
  summarize(
    mean = mean(ConcPerCaseRate))

  SARSConcPerCase  %>%
  group_by(`WWTPName`) %>%
  get_summary_stats(Conc_Capita, type = "mean_sd")

t.test(Conc_Capita ~ WWTPName, data = SARSConcPerCase, paired = TRUE)

#box plot comparison
ggplot(SARSConcPerCase, aes(Date, Conc_Capita)) +
  geom_boxplot(aes(colour=`WWTPName`)) +
  scale_y_continuous() +
   facet_wrap( ~ `WWTPName`) +
  ylab("Copies per Case") +
  theme(axis.title.x = element_blank()) +
  ggtitle("Average SARS-CoV-2 Copies per Case")

```



#Warm versus cold months - SS copies/case 
```{r echo=FALSE}

##temperature based (warmest versus coolest months) comparison of SARS-CoV-2 load

SS_Ave_Temp<-subset(SARSConcPerCase, WWTPName == "Milwaukee South Shore")
#SS_Ave_Temp$Month <-as.character(SS_Ave_Temp$Month)
SS_Ave_Temp_Warm<-subset(SS_Ave_Temp, Month == "Aug" | Month == "Sept" | Month == "Oct")
SS_Ave_Temp_Warm$Month <- factor(SS_Ave_Temp_Warm$Month, levels=c("Aug", "Sept", "Oct"))
SS_Ave_Temp_Cold<-subset(SS_Ave_Temp, Month == "Feb" | Month == "March" | Month == "April")
SS_Ave_Temp_Cold$Month <- factor(SS_Ave_Temp_Cold$Month, levels=c("Feb", "March", "April"))


# Basic box plot
SummerBOXPlot <- ggplot (SS_Ave_Temp_Warm, aes(x = Month, y = Conc_Capita)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Aug" = "orangered1","Sept" = "red4", "Oct" = "orange"))+
   ylab(label = "SARS CoV-2 Copies per Case") + xlab(label = "") +
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("SS Warm Months")

# Basic box plot
WinterBOXPlot <- ggplot (SS_Ave_Temp_Cold, aes(x = Month, y = Conc_Capita)) + 
  geom_boxplot(aes(colour=`Month`))+
     ylab(label = "SARS-Cov-2 Copies per Case") + xlab(label = "") +
  scale_color_manual (values=c("Feb" = "steelblue2","March" = "royalblue3", "April" = "lightskyblue2"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("SS Cold Months")

#both plots together - compare warm vs cold
plot_grid(SummerBOXPlot + ylim(0, 225000), WinterBOXPlot + ylim(0, 225000), ncol = 2) + ggtitle("Warmest Versus Coldest Months SS")

###ANOVA
# Warm
aov.warm <- aov(Conc_Capita ~ as.factor(Month), data = subset(SS_Ave_Temp, Month %in% c("Aug","Sept","Oct")))
plot(aov.warm)
summary(aov.warm)
TukeyHSD(aov.warm)

# Cold
aov.cold <- aov(Conc_Capita ~ as.factor(Month), data = subset(SS_Ave_Temp, Month %in% c("Feb","March","April")))
plot(aov.cold)
summary(aov.cold)
TukeyHSD(aov.cold)

#create usable data for t-test
SS_Ave_Temp_Warm$Type<-"warm"
SS_Ave_Temp_Cold$Type<-"cold"
data.wwtp<-rbind(SS_Ave_Temp_Warm, SS_Ave_Temp_Cold)

#perform t-test (not paired due to uneven values in warm and cold datasets)
t.test(Conc_Capita ~ Type, paired = FALSE, data=data.wwtp)

```


#PARAMETERS
```{r echo=FALSE}

###DAILY AVERAGE TEMP (C)
#visual comparison
ggplot(SARSConcPerCase, aes(Date, AveTemp)) +
  geom_point(aes(colour=`WWTPName`)) +
  facet_wrap( ~ `WWTPName`) +
  ggtitle("Daily average Temperature")

#create statistical data for t-test
SARSConcPerCase  %>%
  group_by(`WWTPName`) %>%
  get_summary_stats(AveTemp, type = "mean_sd")

#paired ttest (JI and SS plants/ same day/ same general conditions)
t.test(AveTemp ~ WWTPName, data = SARSConcPerCase, paired = TRUE)



###AVERAGE FLOW RATE (MGD)
#visual comparison
ggplot(SARSConcPerCase, aes(Date, AveFlowRate)) +
  geom_point(aes(colour=`WWTPName`)) +
  facet_wrap( ~ `WWTPName`) +
  ggtitle("Average Flow Rate")

#create statistical data for t-test
SARSConcPerCase  %>%
  group_by(`WWTPName`) %>%
  get_summary_stats(AveFlowRate, type = "mean_sd")

#paired ttest (JI and SS plants/ same day/ same general conditions)
t.test(AveFlowRate ~ WWTPName, data = SARSConcPerCase, paired = TRUE)

###TSS (MG/L)
#visual comparison
ggplot(SARSConcPerCase, aes(Date, TSS)) +
  geom_point(aes(colour=`WWTPName`)) +
  facet_wrap( ~ `WWTPName`) +
  ggtitle("Daily TSS")

#create statistical data for t-test
SARSConcPerCase  %>%
  group_by(`WWTPName`) %>%
  get_summary_stats(TSS, type = "mean_sd")

#paired ttest (JI and SS plants/ same day/ same general conditions)
t.test(TSS ~ WWTPName, data = SARSConcPerCase, paired = TRUE)

###BOD
#visual comparison
ggplot(SARSConcPerCase, aes(Date, BOD)) +
  geom_point(aes(colour=`WWTPName`)) +
  facet_wrap( ~ `WWTPName`) +
  ggtitle("Daily BOD")

#create statistical data for t-test
SARSConcPerCase  %>%
  group_by(`WWTPName`) %>%
  get_summary_stats(BOD, type = "mean_sd")

#paired ttest (JI and SS plants/ same day/ same general conditions)
t.test(BOD ~ WWTPName, data = SARSConcPerCase, paired = TRUE)

```

###SS Parameters
```{r echo=FALSE}

##temperature based (warmest versus coolest months) comparison of various WWTP parameters

### TEMPERATURE
SummerTemp <- ggplot (SS_Ave_Temp_Warm, aes(x = Month, y = AveTemp)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Aug" = "orangered1","Sept" = "red4", "Oct" = "orange"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("SS Monthly Average Temperature - Warm Months")

WinterTemp <- ggplot (SS_Ave_Temp_Cold, aes(x = Month, y = AveTemp)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Feb" = "steelblue2","March" = "royalblue3", "April" = "lightskyblue2"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("SS Monthly Temperature - Cold Months")

#both plots together - compare warm vs cold
plot_grid(SummerTemp + ylim(5,20), WinterTemp + ylim(5,20), ncol = 2) + ggtitle("Warmest Versus Coldest Months - Temp")

###ANOVA for comparison of variables in each group (hot v. cold)
# Warm
temp.warm <- aov(AveTemp ~ as.factor(Month), data = subset(SS_Ave_Temp, Month %in% c("Aug","Sept","Oct")))
#plot(flow.warm)
summary(temp.warm)
TukeyHSD(temp.warm)

# Cold
temp.cold <- aov(AveTemp ~ as.factor(Month), data = subset(SS_Ave_Temp, Month %in% c("Feb","March","April")))
#plot(flow.cold)
summary(temp.cold)
TukeyHSD(temp.cold)

#create usable data for t-test
SS_Ave_Temp_Warm$Type<-"warm"
SS_Ave_Temp_Cold$Type<-"cold"
data.wwtpSS<-rbind(SS_Ave_Temp_Warm, SS_Ave_Temp_Cold)

#perform Welch's t-test (not paired due to uneven values in hot v. cold data sets)
t.test(AveTemp ~ Type, paired = FALSE, data=data.wwtpSS)


###CASE RATE
SummerCRSS <- ggplot (SS_Ave_Temp_Warm, aes(x = Month, y = case_rate)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Aug" = "orangered1","Sept" = "red4", "Oct" = "orange"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("SS Case Rate - Warm Months")

WinterCRSS <- ggplot (SS_Ave_Temp_Cold, aes(x = Month, y = case_rate)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Feb" = "steelblue2","March" = "royalblue3", "April" = "lightskyblue2"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("SS Case Rate - Cold Months")

#both plots together - compare warm vs cold
plot_grid(SummerCRSS, WinterCRSS, ncol = 2) + ggtitle("Warmest Versus Coldest Months - Case Rate")

###ANOVA
# Warm
CR.warmSS <- aov(case_rate ~ as.factor(Month), data = subset(SS_Ave_Temp, Month %in% c("Aug","Sept","Oct")))
#plot(flow.warmJI)
summary(CR.warmSS)
TukeyHSD(CR.warmSS)

# Cold
CR.coldSS <- aov(case_rate ~ as.factor(Month), data = subset(SS_Ave_Temp, Month %in% c("Feb","March","April")))
#plot(flow.coldJI)
summary(CR.coldSS)
TukeyHSD(CR.coldSS)

#perform t-test (not paired due to uneven values)
t.test(case_rate ~ Type, paired = FALSE, data=data.wwtpSS)



### DAILY AVERAGE FLOW
SummerFlow <- ggplot (SS_Ave_Temp_Warm, aes(x = Month, y = AveFlowRate)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Aug" = "orangered1","Sept" = "red4", "Oct" = "orange"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("SS Flow - Warm Months")

WinterFlow <- ggplot (SS_Ave_Temp_Cold, aes(x = Month, y = AveFlowRate)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Feb" = "steelblue2","March" = "royalblue3", "April" = "lightskyblue2"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("SS Flow - Cold Months")

#both plots together - compare warm vs cold
plot_grid(SummerFlow + ylim(0,200), WinterFlow + ylim(0,200), ncol = 2) + ggtitle("Warmest Versus Coldest Months - Flow")

###ANOVA
# Warm
flow.warm <- aov(AveFlowRate ~ as.factor(Month), data = subset(SS_Ave_Temp, Month %in% c("Aug","Sept","Oct")))
#plot(flow.warm)
summary(flow.warm)
TukeyHSD(flow.warm)

# Cold
flow.cold <- aov(AveFlowRate ~ as.factor(Month), data = subset(SS_Ave_Temp, Month %in% c("Feb","March","April")))
#plot(flow.cold)
summary(flow.cold)
TukeyHSD(flow.cold)

#perform t-test (not paired due to uneven values)
t.test(AveFlowRate ~ Type, paired = FALSE, data=data.wwtpSS)




### TSS
SummerTSS <- ggplot (SS_Ave_Temp_Warm, aes(x = Month, y = TSS)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Aug" = "orangered1","Sept" = "red4", "Oct" = "orange"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("SS TSS - Warm Months")

WinterTSS <- ggplot (SS_Ave_Temp_Cold, aes(x = Month, y = TSS)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Feb" = "steelblue2","March" = "royalblue3", "April" = "lightskyblue2"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("SS TSS - Cold Months")

#both plots together - compare warm vs cold
plot_grid(SummerTSS+ ylim(0,500), WinterTSS+ ylim(0,500), ncol = 2) + ggtitle("Warmest Versus Coldest Months - TSS")

###ANOVA
# Warm
TSS.warm <- aov(TSS ~ as.factor(Month), data = subset(SS_Ave_Temp, Month %in% c("Aug","Sept","Oct")))
#plot(TSS.warm)
summary(TSS.warm)
TukeyHSD(TSS.warm)

# Cold
TSS.cold <- aov(TSS ~ as.factor(Month), data = subset(SS_Ave_Temp, Month %in% c("Feb","March","April")))
#plot(TSS.cold)
summary(TSS.cold)
TukeyHSD(TSS.cold)

#perform t-test (not paired due to uneven values)
t.test(TSS ~ Type, paired = FALSE, data=data.wwtpSS)




### BOD
SummerBOD <- ggplot (SS_Ave_Temp_Warm, aes(x = Month, y = BOD)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Aug" = "orangered1","Sept" = "red4", "Oct" = "orange"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("SS BOD - Warm Months")

WinterBOD <- ggplot (SS_Ave_Temp_Cold, aes(x = Month, y = BOD)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Feb" = "steelblue2","March" = "royalblue3", "April" = "lightskyblue2"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("SS BOD - Cold Months")

#both plots together - compare warm vs cold
plot_grid(SummerBOD+ ylim(0,650), WinterBOD+ ylim(0,650), ncol = 2) + ggtitle("Warmest Versus Coldest Months - BOD")

###ANOVA
# Warm
BOD.warm <- aov(BOD ~ as.factor(Month), data = subset(SS_Ave_Temp, Month %in% c("Aug","Sept","Oct")))
#plot(BOD.warm)
summary(BOD.warm)
TukeyHSD(BOD.warm)

# Cold
BOD.cold <- aov(BOD ~ as.factor(Month), data = subset(SS_Ave_Temp, Month %in% c("Feb","March","April")))
#plot(BOD.cold)
summary(BOD.cold)
TukeyHSD(BOD.cold)

#perform t-test (not paired due to uneven values)
t.test(BOD ~ Type, paired = FALSE, data=data.wwtpSS)
```


#Warm versus cold months - JI copies/case 
```{r echo=FALSE}

##temperature based (warmest versus coolest months) comparison of SARS-CoV-2 load
#processed the same as SS parameters

JI_Ave_Temp<-subset(SARSConcPerCase, WWTPName == "Milwaukee Jones Island")
JI_Ave_Temp_Warm<-subset(JI_Ave_Temp, Month == "Aug" | Month == "Sept" | Month == "Oct")
JI_Ave_Temp_Warm$Month <- factor(JI_Ave_Temp_Warm$Month, levels=c("Aug", "Sept", "Oct"))
JI_Ave_Temp_Cold<-subset(JI_Ave_Temp, Month == "Feb" | Month == "March" | Month == "April")
JI_Ave_Temp_Cold$Month <- factor(JI_Ave_Temp_Cold$Month, levels=c("Feb", "March", "April"))

# Basic box plot
JISummerBOXPlot <- ggplot (JI_Ave_Temp_Warm, aes(x = Month, y = Conc_Capita)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Aug" = "orangered1","Sept" = "red4", "Oct" = "orange"))+
     ylab(label = "Copies per Case") + xlab(label = "") +
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("JI Warm Months")

# Basic box plot
JIWinterBOXPlot <- ggplot (JI_Ave_Temp_Cold, aes(x = Month, y = Conc_Capita)) + 
  geom_boxplot(aes(colour=`Month`))+
     ylab(label = "Copies per Case") + xlab(label = "") +
  scale_color_manual (values=c("Feb" = "steelblue2","March" = "royalblue3", "April" = "lightskyblue2"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("JI Cold Months")

#both plots together - compare warm vs cold
plot_grid(JISummerBOXPlot + ylim(0, 225000), JIWinterBOXPlot + ylim(0, 225000), ncol = 2) + ggtitle("Warmest Versus Coldest Months SS")

###ANOVA
# Warm
aov.warm <- aov(Conc_Capita ~ as.factor(Month), data = subset(JI_Ave_Temp, Month %in% c("Aug","Sept","Oct")))
#plot(aov.warm)
summary(aov.warm)
TukeyHSD(aov.warm)

# Cold
aov.cold <- aov(Conc_Capita ~ as.factor(Month), data = subset(JI_Ave_Temp, Month %in% c("Feb","March","April")))
#plot(aov.cold)
summary(aov.cold)
TukeyHSD(aov.cold)

#create usable data for t-test
JI_Ave_Temp_Warm$Type<-"warm"
JI_Ave_Temp_Cold$Type<-"cold"
JI.data.wwtp<-rbind(JI_Ave_Temp_Warm, JI_Ave_Temp_Cold)

#perform t-test (not paired due to uneven values)
t.test(Conc_Capita ~ Type, paired = FALSE, data=JI.data.wwtp)
```

###JI Parameters
```{r echo=FALSE}

##temperature based (warmest versus coolest months) comparison of various WWTP parameters

###DAILY AVERAGE TEMPERATURE
SummertempJI <- ggplot (JI_Ave_Temp_Warm, aes(x = Month, y = AveTemp)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Aug" = "orangered1","Sept" = "red4", "Oct" = "orange"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("JI Monthly Average Temperature - Warm Months")

WintertempJI <- ggplot (JI_Ave_Temp_Cold, aes(x = Month, y = AveTemp)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Feb" = "steelblue2","March" = "royalblue3", "April" = "lightskyblue2"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("JI Monthly Temperature - Cold Months")

#both plots together - compare warm vs cold
plot_grid(SummertempJI + ylim(5,20), WintertempJI + ylim(5,20), ncol = 2) + ggtitle("Warmest Versus Coldest Months - Temps")

###ANOVA
# Warm
temp.warmJI <- aov(AveTemp ~ as.factor(Month), data = subset(JI_Ave_Temp, Month %in% c("Aug","Sept","Oct")))
#plot(flow.warmJI)
summary(temp.warmJI)
TukeyHSD(temp.warmJI)

# Cold
temp.coldJI <- aov(AveTemp ~ as.factor(Month), data = subset(JI_Ave_Temp, Month %in% c("Feb","March","April")))
#plot(flow.coldJI)
summary(temp.coldJI)
TukeyHSD(temp.coldJI)

#perform t-test (not paired due to uneven values)
t.test(AveTemp ~ Type, paired = FALSE, data=JI.data.wwtp)




#CASE RATE
SummerCRJI <- ggplot (JI_Ave_Temp_Warm, aes(x = Month, y = case_rate)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Aug" = "orangered1","Sept" = "red4", "Oct" = "orange"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("JI Case Rate - Warm Months")

WinterCRJI <- ggplot (JI_Ave_Temp_Cold, aes(x = Month, y = case_rate)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Feb" = "steelblue2","March" = "royalblue3", "April" = "lightskyblue2"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("JI Case Rate - Cold Months")

#both plots together - compare warm vs cold
plot_grid(SummerCRJI, WinterCRJI, ncol = 2) + ggtitle("Warmest Versus Coldest Months - Temps")

###ANOVA
# Warm
CR.warmJI <- aov(case_rate ~ as.factor(Month), data = subset(JI_Ave_Temp, Month %in% c("Aug","Sept","Oct")))
#plot(flow.warmJI)
summary(temp.warmJI)
TukeyHSD(temp.warmJI)

# Cold
CR.coldJI <- aov(case_rate ~ as.factor(Month), data = subset(JI_Ave_Temp, Month %in% c("Feb","March","April")))
#plot(flow.coldJI)
summary(CR.coldJI)
TukeyHSD(CR.coldJI)

#perform t-test (not paired due to uneven values)
t.test(case_rate ~ Type, paired = FALSE, data=JI.data.wwtp)



### DAILY AVERAGE FLOW
SummerFlowJI <- ggplot (JI_Ave_Temp_Warm, aes(x = Month, y = AveFlowRate)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Aug" = "orangered1","Sept" = "red4", "Oct" = "orange"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("JI Flow - Warm Months")

WinterFlowJI <- ggplot (JI_Ave_Temp_Cold, aes(x = Month, y = AveFlowRate)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Feb" = "steelblue2","March" = "royalblue3", "April" = "lightskyblue2"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("JI Flow - Cold Months")

#both plots together - compare warm vs cold
plot_grid(SummerFlowJI + ylim(0,300), WinterFlowJI + ylim(0,300), ncol = 2) + ggtitle("Warmest Versus Coldest Months - Flow")

###ANOVA
# Warm
flow.warmJI <- aov(AveFlowRate ~ as.factor(Month), data = subset(JI_Ave_Temp, Month %in% c("Aug","Sept","Oct")))
#plot(flow.warmJI)
summary(flow.warmJI)
TukeyHSD(flow.warmJI)

# Cold
flow.coldJI <- aov(AveFlowRate ~ as.factor(Month), data = subset(JI_Ave_Temp, Month %in% c("Feb","March","April")))
#plot(flow.coldJI)
summary(flow.coldJI)
TukeyHSD(flow.coldJI)

#perform t-test (not paired due to uneven values)
t.test(AveFlowRate ~ Type, paired = FALSE, data=JI.data.wwtp)



### TSS
SummerTSSJI <- ggplot (JI_Ave_Temp_Warm, aes(x = Month, y = TSS)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Aug" = "orangered1","Sept" = "red4", "Oct" = "orange"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("JI TSS - Warm Months")

WinterTSSJI <- ggplot (JI_Ave_Temp_Cold, aes(x = Month, y = TSS)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Feb" = "steelblue2","March" = "royalblue3", "April" = "lightskyblue2"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("JI TSS - Cold Months")

#both plots together - compare warm vs cold
plot_grid(SummerTSSJI + ylim(0,500), WinterTSSJI + ylim(0,500), ncol = 2) + ggtitle("Warmest Versus Coldest Months - TSS")

###ANOVA
# Warm
TSS.warmJI <- aov(TSS ~ as.factor(Month), data = subset(JI_Ave_Temp, Month %in% c("Aug","Sept","Oct")))
#plot(TSS.warmJI)
summary(TSS.warmJI)
TukeyHSD(TSS.warmJI)

# Cold
TSS.coldJI <- aov(TSS ~ as.factor(Month), data = subset(JI_Ave_Temp, Month %in% c("Feb","March","April")))
#plot(TSS.coldJI)
summary(TSS.coldJI)
TukeyHSD(TSS.coldJI)

#perform t-test (not paired due to uneven values)
t.test(TSS ~ Type, paired = FALSE, data=JI.data.wwtp)




### BOD
SummerBODJI <- ggplot (JI_Ave_Temp_Warm, aes(x = Month, y = BOD)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Aug" = "orangered1","Sept" = "red4", "Oct" = "orange"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("JI BOD - Warm Months")

WinterBODJI <- ggplot (JI_Ave_Temp_Cold, aes(x = Month, y = BOD)) + 
  geom_boxplot(aes(colour=`Month`))+
  scale_color_manual (values=c("Feb" = "steelblue2","March" = "royalblue3", "April" = "lightskyblue2"))+
  theme(axis.ticks.x = element_blank(),
        legend.position = "None") + ggtitle("JI BOD - Cold Months")

#both plots together - compare warm vs cold
plot_grid(SummerBODJI+ ylim(0,550), WinterBODJI + ylim(0,550), ncol = 2) + ggtitle("Warmest Versus Coldest Months - BOD")

###ANOVA
# Warm
BOD.warmJI <- aov(BOD ~ as.factor(Month), data = subset(JI_Ave_Temp, Month %in% c("Aug","Sept","Oct")))
#plot(BOD.warmJI)
summary(BOD.warmJI)
TukeyHSD(BOD.warmJI)

# Cold
BOD.coldJI <- aov(BOD ~ as.factor(Month), data = subset(JI_Ave_Temp, Month %in% c("Feb","March","April")))
#plot(BOD.coldJI)
summary(BOD.coldJI)
TukeyHSD(BOD.coldJI)

#perform t-test (not paired due to uneven values)
t.test(BOD ~ Type, paired = FALSE, data=JI.data.wwtp)
```


###Visual Comparison 
```{r echo=FALSE}

##combine plots for easier visual comparison

#SS vs JI copies/case warm vs cold
plot_grid(SummerBOXPlot + ylim(0, 225000), WinterBOXPlot + ylim(0, 225000),JISummerBOXPlot + ylim(0, 225000), JIWinterBOXPlot + ylim(0, 225000), ncol = 2, nrow=2)  #+ draw_label("SARS-CoV-2 Concentration per Case During Warmest and Coldest Months in SS and JI WWTPs")


#SS vs JI temp warm vs cold
plot_grid(SummerTemp + ylim(7,20), WinterTemp + ylim(7,20), SummertempJI + ylim(7,20), WintertempJI + ylim(7,20), ncol = 2, nrow = 2) + ggtitle("Average Temperature")

#SS vs JI flow warm vs cold
plot_grid(SummerFlow + ylim(0,300), WinterFlow + ylim(0,300), SummerFlowJI + ylim(0,300), WinterFlowJI + ylim(0,300), ncol = 2, nrow=2) + ggtitle("Daily Average Flow")

#SS vs JI TSS warm vs cold
plot_grid(SummerTSS+ ylim(0,500), WinterTSS+ ylim(0,500),SummerTSSJI + ylim(0,500), WinterTSSJI+ ylim(0,500), ncol = 2, nrow=2) + ggtitle("TSS")

#SS vs JI BOD warm vs cold
plot_grid(SummerBOD+ ylim(0,650), WinterBOD+ ylim(0,650),SummerBODJI+ ylim(0,650), WinterBODJI + ylim(0,650), ncol = 2, nrow = 2) + ggtitle("BOD")

#SS vs. JI case rate warm vs cold
plot_grid(SummerCRSS + ylim(0, 100), WinterCRSS + ylim(0, 100),SummerCRJI + ylim(0, 100), WinterCRJI + ylim(0, 100), ncol = 2, nrow=2)  #+ draw_label("SARS-CoV-2 Concentration per Case During Warmest and Coldest Months in SS and JI WWTPs")

```


### ttest between JI hot and SS hot
```{r echo=FALSE}

t.test(SS_Ave_Temp_Warm$Conc_Capita, JI_Ave_Temp_Warm$Conc_Capita, paired = FALSE)
t.test(SS_Ave_Temp_Cold$Conc_Capita, JI_Ave_Temp_Cold$Conc_Capita, paired = FALSE)
t.test(SS_Ave_Temp_Warm$AveTemp, JI_Ave_Temp_Warm$AveTemp, paired = FALSE)
t.test(SS_Ave_Temp_Cold$AveTemp, JI_Ave_Temp_Cold$AveTemp, paired = FALSE)
t.test(SS_Ave_Temp_Warm$case_rate, JI_Ave_Temp_Warm$case_rate, paired = FALSE)
t.test(SS_Ave_Temp_Cold$case_rate, JI_Ave_Temp_Cold$case_rate, paired = FALSE)
t.test(SS_Ave_Temp_Warm$AveFlowRate, JI_Ave_Temp_Warm$AveFlowRate, paired = FALSE)
t.test(SS_Ave_Temp_Cold$AveFlowRate, JI_Ave_Temp_Cold$AveFlowRate, paired = FALSE)
t.test(SS_Ave_Temp_Warm$BOD, JI_Ave_Temp_Warm$BOD, paired = FALSE)
t.test(SS_Ave_Temp_Cold$BOD, JI_Ave_Temp_Cold$BOD, paired = FALSE)
t.test(SS_Ave_Temp_Warm$TSS, JI_Ave_Temp_Warm$TSS, paired = FALSE)
t.test(SS_Ave_Temp_Cold$TSS, JI_Ave_Temp_Cold$TSS, paired = FALSE)

```


### correlation in SS  (kendalls)
```{r echo=FALSE}

##correlation of various parameters to SARS-CoV-2 copies/case using Kendall's tau
#additional flow analysis in separate rmd (flow_comparison)

#warm months only
cor.test(SS_Ave_Temp_Warm$Conc_Capita, SS_Ave_Temp_Warm$AveTemp, method=c("kendall"))
# ggscatter(SS_Ave_Temp_Warm, x = "Conc_Capita", y = "AveTemp", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Copies per Case", ylab = "Ave Temp")

cor.test(SS_Ave_Temp_Warm$Conc_Capita, SS_Ave_Temp_Warm$AveFlowRate, method=c("kendall"))
cor.test(SS_Ave_Temp_Warm$Conc_Case, SS_Ave_Temp_Warm$AveFlowRate, method=c("kendall"))
# ggscatter(SS_Ave_Temp_Warm, x = "Conc_Capita", y = "AveFlowRate",
#           add = "reg.line", conf.int = TRUE,
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Concentration per Case", ylab = "Ave Flow Rate")

cor.test(SS_Ave_Temp_Warm$Conc_Capita, SS_Ave_Temp_Warm$BOD, method=c("kendall"))
# ggscatter(SS_Ave_Temp_Warm, x = "Conc_Capita", y = "BOD", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Copies per Case", ylab = "BOD")

cor.test(SS_Ave_Temp_Warm$Conc_Capita, SS_Ave_Temp_Warm$TSS, method=c("kendall"))
# ggscatter(SS_Ave_Temp_Warm, x = "Conc_Capita", y = "TSS", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Copies per Case", ylab = "TSS (mg/L)")



###cold months only
cor.test(SS_Ave_Temp_Cold$Conc_Capita, SS_Ave_Temp_Cold$AveTemp, method=c("kendall"))
# ggscatter(SS_Ave_Temp_Cold, x = "Conc_Capita", y = "AveTemp", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Copies per Case", ylab = "Ave Temp")

cor.test(SS_Ave_Temp_Cold$Conc_Capita, SS_Ave_Temp_Cold$AveFlowRate, method=c("kendall"))
cor.test(SS_Ave_Temp_Cold$Conc_Case, SS_Ave_Temp_Cold$AveFlowRate, method=c("kendall"))
# ggscatter(SS_Ave_Temp_Cold, x = "Conc_Capita", y = "AveFlowRate",
#           add = "reg.line", conf.int = TRUE,
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Concentration", ylab = "Ave Flow Rate")

cor.test(SS_Ave_Temp_Cold$Conc_Capita, SS_Ave_Temp_Cold$BOD, method=c("kendall"))
# ggscatter(SS_Ave_Temp_Cold, x = "Conc_Capita", y = "BOD", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Concentration per Case", ylab = "BOD")

cor.test(SS_Ave_Temp_Cold$Conc_Capita, SS_Ave_Temp_Cold$TSS, method=c("kendall"))
# ggscatter(SS_Ave_Temp_Cold, x = "Conc_Capita", y = "TSS", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Concentration per Case", ylab = "TSS (mg/L)")


###TOTAL DATA SET (SS)
cor.test(SS_Ave_Temp$Conc_Capita, SS_Ave_Temp$AveTemp, method=c("kendall"))
ggscatter(SS_Ave_Temp_Cold, x = "Conc_Capita", y = "AveTemp", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "Ave Temp (C)")

cor.test(SS_Ave_Temp$Conc_Capita, SS_Ave_Temp$BOD, method=c("kendall"))
ggscatter(SS_Ave_Temp, x = "Conc_Capita", y = "BOD", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "BOD (mg/L)")

cor.test(SS_Ave_Temp$Conc_Capita, SS_Ave_Temp$TSS, method=c("kendall"))
ggscatter(SS_Ave_Temp, x = "Conc_Capita", y = "TSS", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "TSS (mg/L)")

cor.test(SS_Ave_Temp$Conc_Capita, SS_Ave_Temp$case_rate, method=c("kendall"))
ggscatter(SS_Ave_Temp, x = "Conc_Capita", y = "case_rate", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "Case Rate per 100,000")

### Flow correlation to SARS-CoV-2 load (copies/case)
cor.test(SS_Ave_Temp$Conc_Capita, SS_Ave_Temp$AveFlowRate, method=c("kendall"))
ggscatter(SS_Ave_Temp, x = "Conc_Capita", y = "AveFlowRate", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "Ave Flow Rate (MGD)")

### Flow correlation to SARS-CoV-2 concentration (concentration/case)
cor.test(SS_Ave_Temp$Conc_Case, SS_Ave_Temp$AveFlowRate, method=c("kendall"))
ggscatter(SS_Ave_Temp, x = "Conc_Case", y = "AveFlowRate", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Concentration per Case", ylab = "Ave Flow Rate")

```


### correlation in JI  (kendalls)
```{r echo=FALSE}

##correlation of various parameters to SARS-CoV-2 copies/case using Kendall's tau

#warm months only
cor.test(JI_Ave_Temp_Warm$Conc_Capita, JI_Ave_Temp_Warm$AveTemp, method=c("kendall"))
# ggscatter(JI_Ave_Temp_Warm, x = "Conc_Capita", y = "AveTemp", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Concentration per Case", ylab = "Ave Temp")

cor.test(JI_Ave_Temp_Warm$Conc_Capita, JI_Ave_Temp_Warm$AveFlowRate, method=c("kendall"))
# ggscatter(JI_Ave_Temp_Warm, x = "Conc_Capita", y = "AveFlowRate", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Concentration per Case", ylab = "Ave Flow Rate")

cor.test(JI_Ave_Temp_Warm$Conc_Capita, JI_Ave_Temp_Warm$BOD, method=c("kendall"))
# ggscatter(JI_Ave_Temp_Warm, x = "Conc_Capita", y = "BOD", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Concentration per Case", ylab = "BOD")

cor.test(JI_Ave_Temp_Warm$Conc_Capita, JI_Ave_Temp_Warm$TSS, method=c("kendall"))
# ggscatter(JI_Ave_Temp_Warm, x = "Conc_Capita", y = "TSS", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Concentration per Case", ylab = "TJI")



###cold months only
cor.test(JI_Ave_Temp_Cold$Conc_Capita, JI_Ave_Temp_Cold$AveTemp, method=c("kendall"))
# #ggscatter(JI_Ave_Temp_Cold, x = "Conc_Capita", y = "AveTemp", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Concentration per Case", ylab = "Ave Temp")

cor.test(JI_Ave_Temp_Cold$Conc_Capita, JI_Ave_Temp_Cold$AveFlowRate, method=c("kendall"))
# ggscatter(JI_Ave_Temp_Cold, x = "Conc_Capita", y = "AveFlowRate", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Concentration per Case", ylab = "Ave Flow Rate")

cor.test(JI_Ave_Temp_Cold$Conc_Capita, JI_Ave_Temp_Cold$BOD, method=c("kendall"))
# ggscatter(JI_Ave_Temp_Cold, x = "Conc_Capita", y = "BOD", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Concentration per Case", ylab = "BOD")

cor.test(JI_Ave_Temp_Cold$Conc_Capita, JI_Ave_Temp_Cold$TSS, method=c("kendall"))
# ggscatter(JI_Ave_Temp_Cold, x = "Conc_Capita", y = "TSS", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "kendall",
#           xlab = "SARS-CoV-2 Concentration per Case", ylab = "TJI")


###TOTAL DATA SET (JI)
#Kendall's tau empirical p-values and visual represtentation

cor.test(JI_Ave_Temp$Conc_Capita, JI_Ave_Temp$AveTemp, method=c("kendall"))
ggscatter(JI_Ave_Temp, x = "Conc_Capita", y = "AveTemp", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "Ave Temp (C)")

cor.test(JI_Ave_Temp$Conc_Capita, JI_Ave_Temp$BOD, method=c("kendall"))
 ggscatter(JI_Ave_Temp, x = "Conc_Capita", y = "BOD", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "BOD (mg/L)")

cor.test(JI_Ave_Temp$Conc_Capita, JI_Ave_Temp$TSS, method=c("kendall"))
ggscatter(JI_Ave_Temp, x = "Conc_Capita", y = "TSS", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "TSS (mg/L)")

cor.test(JI_Ave_Temp$Conc_Capita, JI_Ave_Temp$case_rate, method=c("kendall"))
ggscatter(JI_Ave_Temp, x = "Conc_Capita", y = "case_rate", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "Case Rate per 100,000")

### Flow correlation to SARS-CoV-2 load (copiesn/case)
cor.test(JI_Ave_Temp$Conc_Capita, JI_Ave_Temp$AveFlowRate, method=c("kendall"))
ggscatter(JI_Ave_Temp, x = "Conc_Capita", y = "AveFlowRate", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "Ave Flow Rate (MGD)")

### Flow correlation to SARS-CoV-2 concentration (concentration/case)
cor.test(JI_Ave_Temp$Conc_Case, JI_Ave_Temp$AveFlowRate, method=c("kendall"))
ggscatter(JI_Ave_Temp, x = "Conc_Case", y = "AveFlowRate", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Concentration per Case", ylab = "Ave Flow Rate (MGD)")
```

####JI AND SS
```{r echo=FALSE}
###TOTAL DATA SET (SS)
#Kendall's tau empirical p-values and visual representation

cor.test(SARSConcPerCase$Conc_Capita, SARSConcPerCase$AveTemp, method=c("kendall"))
ggscatter(SARSConcPerCase, x = "Conc_Capita", y = "AveTemp", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "Ave Temp (C)")

cor.test(SARSConcPerCase$Conc_Capita, SARSConcPerCase$BOD, method=c("kendall"))
 ggscatter(SARSConcPerCase, x = "Conc_Capita", y = "BOD", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "BOD (mg/L)")

cor.test(SARSConcPerCase$Conc_Capita, SARSConcPerCase$TSS, method=c("kendall"))
ggscatter(SARSConcPerCase, x = "Conc_Capita", y = "TSS", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "TSS (mg/L)")

cor.test(SARSConcPerCase$Conc_Capita, SARSConcPerCase$case_rate, method=c("kendall"))
ggscatter(SARSConcPerCase, x = "Conc_Capita", y = "case_rate", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "Case Rate per 100,000")

### Flow correlation to SARS-CoV-2 load (copies/case)
cor.test(SARSConcPerCase$Conc_Capita, SARSConcPerCase$AveFlowRate, method=c("kendall"))
ggscatter(SARSConcPerCase, x = "Conc_Capita", y = "AveFlowRate", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Copies per Case", ylab = "Ave Flow Rate (MGD)")

### Flow correlation to SARS-CoV-2 concentration (concentration/case)
cor.test(SARSConcPerCase$Conc_Case, SARSConcPerCase$AveFlowRate, method=c("kendall"))
ggscatter(SARSConcPerCase, x = "Conc_Case", y = "AveFlowRate", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "SARS-CoV-2 Concentration per Case", ylab = "Ave Flow Rate (MGD)")
```


```{r echo=FALSE}

## Comparison of PMMoV concenrtaion/L wastewater to daily average flow rate
# to determine how human fecal load varies with flow

###TOTAL DATA SET
cor.test(SARSConcPerCase$PPMoVConc, SARSConcPerCase$AveFlowRate, method=c("kendall"))
ggscatter(SARSConcPerCase, x = "PPMoVConc", y = "AveFlowRate", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          add.params = list(fill = "#FF9999"),
          xlab = "PMMoV Concentration per Liter Wastewater", ylab = "Ave Flow Rate (MGD)")+xlim(0,300000000)

###JI
cor.test(JI_Ave_Temp$PPMoVConc, JI_Ave_Temp$AveFlowRate, method=c("kendall"))
JI.PMMoV <- ggscatter(JI_Ave_Temp, x = "PPMoVConc", y = "AveFlowRate", 
          add = "reg.line", conf.int = TRUE, 
          outlier.shape = NA,
          cor.coef = TRUE, cor.method = "kendall",
          add.params = list(fill = "#FF9999"),
          xlab = "PMMoV Concentration per Liter Wastewater", ylab = "Ave Flow Rate (MGD)")

###SS
cor.test(SS_Ave_Temp$PPMoVConc, SS_Ave_Temp$AveFlowRate, method=c("kendall"))
SS.PMMoV <- ggscatter(SS_Ave_Temp, x = "PPMoVConc", y = "AveFlowRate", 
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "kendall",
          add.params = list(fill = "#FF9999"),
          xlab = "PMMoV Concentration per Liter Wastewater", ylab = "Ave Flow Rate (MGD)")

plot_grid(JI.PMMoV, SS.PMMoV,  nrow=2)  

#remove outliers (two from JI, 1 from SS)
plot_grid(JI.PMMoV+xlim(0,100000000),SS.PMMoV+xlim(0,100000000),  nrow=2)  

#linear slope for PMMoV
JI.lim <- lm(PPMoVConc ~ AveFlowRate, data = JI_Ave_Temp)
summary(JI.lim)
SS.lim <- lm(PPMoVConc ~ AveFlowRate, data = SS_Ave_Temp)
summary(SS.lim)
lim <- lm(PPMoVConc ~ AveFlowRate, data = SARSConcPerCase)
summary(lim)


```